An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-15 VLDB2026/main.tex
change 3.1

	Filtered-DiskANN proposes 2 index variants:  
	1) \textbf{FilteredVamana}, which incrementally builds the graph index by inserting data points and dynamically adding edges, allowing adaptive expansion.  
	2) \textbf{StitchedVamana}, which adopts a batch construction strategy—constructing separate Vamana subgraphs for each attribute, followed by merging and edge pruning.

@@

	\noindent\textbf{\underline{CAPS \cite{CAPS}.}} As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes. CAPS addresses this issue by being the first simultaneous filtering algorithm based on spatial partitioning, significantly reducing index size.

@@

	\noindent\textbf{\underline{ACORN \cite{ACORN}.}}  
	Above simultaneous filtering methods struggle with large-scale, unbounded, or unknown predicate sets.
	%The above simultaneous filtering methods are less effective in scenarios involving large-scale, unbounded, or unknown predicate sets, where a predicate refers to a condition or rule used for filtering. 
	ACORN addresses this issue by introducing a predicate-agnostic indexing framework.

@@

	ACORN includes 2 index variants:  
	1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, increasing memory usage for higher performance.  
	2) \textbf{ACORN-1}, which extends neighbor lists by considering second-hop neighbors during search, reducing index size with minor performance loss.

	\noindent\textbf{\underline{UNG \cite{UNG}.}} Graph-based methods (NHQ, Filtered-DiskANN, ACO-\\RN) do not guarantee result completeness. UNG is proposed to overcome both limitations.

>>>>

	Filtered-DiskANN proposes 2 indexes:  
	1) \textbf{FilteredVamana}, which incrementally builds the graph index by inserting data points and dynamically adding edges, allowing adaptive expansion.  
	2) \textbf{StitchedVamana}, which adopts a batch construction strategy—constructing separate Vamana subgraphs for each attribute, followed by merging and edge pruning.

@@

	\noindent\textbf{\underline{CAPS \cite{CAPS}.}} Different from the above graph-based simultaneous filtering algorithms, CAPS is the first simultaneous filtering algorithm based on spatial partitioning.
	%As graph-based methods, NHQ and Filtered-DiskANN often result in large index sizes. CAPS addresses this issue by being the first simultaneous filtering algorithm based on spatial partitioning, significantly reducing index size.

@@

	\noindent\textbf{\underline{ACORN \cite{ACORN}.}}  
	Above simultaneous filtering algorithms struggle with large-scale, unbounded, or unknown predicate sets.
	%The above simultaneous filtering methods are less effective in scenarios involving large-scale, unbounded, or unknown predicate sets, where a predicate refers to a condition or rule used for filtering. 
	ACORN addresses this issue by introducing a predicate-agnostic indexing framework.

@@

	ACORN includes 2 indexes:  
	1) \textbf{ACORN-$\gamma$}, which expands neighbor lists during construction, increasing memory usage for higher performance.  
	2) \textbf{ACORN-1}, which extends neighbor lists by considering second-hop neighbors during search, reducing index size with minor performance loss.

	\noindent\textbf{\underline{UNG \cite{UNG}.}} The above simultaneous filtering algorithms may not guarantee the completeness of the results and perform poorly when the attribute selectivity is low. UNG is proposed to overcome these limitations.
